Constraints on tensor and scalar couplings from $B\to K\bar\mu\mu$ and $B_s\to \bar\mu\mu$

### 2015-08-05 tensor/draft/draft-tensor-op.tex
[draft] run spellchecker, proof read sec. 4.3

The full dependence of $F_H^\ell$ and $A_{\rm FB}^\ell$ on tensor and
scalar couplings has been presented in \cite{Bobeth:2007dw,
  Bobeth:2012vn}, adopting the effective theory \refeq{eq:Heff},
i.e. neglecting higher-dimensional operators with {$\mbox{dim} \geq
  8$}. These results imply that for SM values of the effective
couplings
\begin{align}
  F_H^\ell(q^2) \big|_{\rm SM} & \propto \frac{m_\ell^2}{q^2}
    {\bigg/ \Gamma_\ell} \,, &
  A_{\rm FB}^\ell \big|_{\rm SM} & = 0 \,.
\end{align}
Hence, for $\ell = e,\, \mu$ both observables are quasi-null tests.
The flat term $F_H^\ell(q^2)|_{\rm SM}$ is strongly suppressed {by
  small lepton masses for the considered kinematical region $1 \leq
  q^2 \leq 22$ GeV$^2$} \cite{Bobeth:2007dw, Bobeth:2011nj,
  Bouchard:2013eph}.  Nonzero values of $A_{\rm FB}^\ell|_{\rm SM}$
can be induced by higher-order QED corrections, which will modify the
simple $\cos\theta_\ell$ dependence of the angular
distribution~\refeq{eq:ang-distr}, however, currently there is no
solid estimate available for this source of SM background\footnote{
  Logarithmically enhanced NLO QED corrections to $B\to X_s
  \bar\ell\ell$~\cite{Huber:2015sra} turn out to be non-negligible
  for angular observables,
  however, analogous corrections to $B\to K \bar\ell\ell$ are partially 
  included in the event simulation of the experimental 
  analysis~\cite{Aaij:2014tfa} via PHOTOS~\cite{Golonka:2005pn}. 
  As proposed in \cite{Gratrex:2015hna}, the measurement of higher
  moments of the decay distribution~\refeq{eq:ang-distr} could give an 
  estimate of the size of higher-order QED corrections, but still
  admixed with contributions of $\mbox{dim} \geq 8$ operators.}. 
This picture does not change in the presence of new physics contributions to
vector and dipole operators $i = 7,7',9,9',10,10'$. On the other hand,
nonvanishing tensor or scalar contributions are enhanced unless the dynamics of
NP implies similar suppression factors, i.e., lepton-Yukawa couplings for
$F_H^\ell$ or $\alpha_e$ in the case of $A_{\rm FB}^\ell$. In particular,
$F_H^\ell$ is very sensitive to tensor couplings (see \refeq{eq:AFB-dependence}
below) and $A_{\rm FB}^\ell$ is sensitive to the interference of tensor and
scalar couplings (see \refeq{eq:FH-dependence} below).

\begin{figure*}
  \setlength{\relwidth}{0.33\textwidth}
  \begin{center}
    \includegraphics[width=\relwidth]{plots/pdf/ct_K_FH1to6}
    \includegraphics[width=\relwidth]{plots/pdf/ct_K_FH15to22}
    \\
    \includegraphics[width=\relwidth]{plots/pdf/ct_K_BR1to6}
    \includegraphics[width=\relwidth]{plots/pdf/ct_K_BR15to22}
    \\
    \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_BR1to6}
    % \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_BR14to16}
    \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_BR16to19}
    \\
    \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_J_1c_plus_J_2c1to6}
    \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_J_1c_plus_J_2c15to19}
    \\
    \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_J_1s_minus_3J_2s1to6}
    \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_J_1s_minus_3J_2s15to19}
  \end{center}
  \caption{ The sensitivity to the tensor coupling
    $\mbox{Re}(\wilson{T})$ of $F_H^\mu$ and {${\cal B}_\mu$} in $B^+
    \to K^+ \bar\mu\mu$ {as well as} {${\cal B}_\mu$},
    $(J_{1c} + J_{2c})$, and $(J_{1s}-3 J_{2s})$ in $B^0 \to K^{*0}
    \bar\mu\mu$. All observables are integrated over $q^2$ bins as
    $\langle \dots \rangle_{[q^2_{\rm min}, q^2_{\rm max}]}$. Angular
    observables are rescaled by the lifetime of the $B$ meson,
    $\tau_B$. The bands represent the theory uncertainties at 68\% and
    95\% probability of the prior predictive.  Two sets of bands are
    shown for $\wilson[NP]{9} = 0$ (blue) and $\wilson[NP]{9} = -1.1$
    (red). If available, the grey band indicates the latest 68\%
    confidence interval reported by LHCb.}
  \label{fig:FHvsCT}
\end{figure*}

@@

For each coupling {that} we vary in a fit, we remain as general as possible, treat it
as a complex number and use the cartesian parametrization assuming uniform
priors for ease of comparison with previous studies. Specifically, we set
\begin{align}
  \label{eq:wilson-prior}
  \mbox{Re}(\wilson{S,S',P,P',T,T5}) &\in [-1, 1],\nn \mbox{Re}(\wilson{9,9',10,10'}) &\in [-7, 7],
\end{align}
and the same for the imaginary parts. The priors of the nuisance parameters are given in \refapp{app:theory:inputs}.

@@

In a scenario with only {complex-valued tensor couplings} $\wilson{T,\, T5}$, the
experimental measurement of $F_H^\mu$ constrains the combination $|\wilson{T}|^2
+ |\wilson{T5}|^2$, up to some small interference of $\wilson{T}$ with vector
couplings $\wilson{7,\,7',\,9,\,9'}$; cf. \refeq{eq:FH-dependence}.  The
according 68\% (95\%) 1D-marginalized probability intervals are listed in the
second column of \reftab{tab:cTT5:1-dimCLs}. From the third column, it is seen
that the constraints become tighter when utilising all observables in
\reftab{tab:observables}, mainly due to the sensitivity of the branching ratio
of $B\to K^{*} \bar\mu\mu$ to tensor couplings (see also
\reffig{fig:FHvsCT}). The latter stronger bounds are driven by the new lattice
results of $B\to K^*$ form factors that predict values above the measured
{ones}~\cite{Horgan:2013pva}. Since tensor couplings contribute constructively
to ${\cal B}(B\to K^{*}\bar\mu\mu)$, large values are better constrained. In
this scenario with vanishing scalar couplings, current measurements of $A_{\rm
  FB}^\mu(B^+\to K^+\bar\mu\mu)$ barely provide any constraint;
cf.~\refeq{eq:AFB-dependence}.

@@

A keen observer may notice that in \reftab{tab:cTT5:1-dimCLs} the SM point
$\wilson{T,T5} \equiv 0$ is contained in every 68\% region in cartesian
coordinates but never in even the 95\% region in polar coordinates\footnote{But
  the bin with lower edge $\wilson{T,T5} = 0$ is always in the 99\%
  region.}. This is a consequence of the general \emph{concentration of
  measure}. Another way to look at it is to transform the uniform prior density
from cartesian to polar coordinates. For the example of a single Wilson
coefficient, say $\wilson{T}$, the transformed density is proportional to the
determinant of the Jacobian which is $|\wilson{T}|$. Since the cartesian prior
boundaries are much larger than the regions of high likelihood, one could think
the value of the boundary is irrelevant, but in fact it determines the peak of
the prior in polar coordinates. In other words, the uniform prior on
$\mbox{Re}(\wilson{T})$ and $\mbox{Im}(\wilson{T})$ favors larger values of
$|\wilson{T}|$ even though we consider it consensus in the community that
smaller rather than larger values are reasonable because $\wilson{T} = 0$ in the
SM. We suggest therefore that the default treatment be revised in the future to
include available prior knowledge.

@@

\begin{figure*}
  \begin{center}
    \includegraphics[width=.325\textwidth]{plots/pdf/scSP_FH,scSP_Bsmumu,sc910SP_K_KstarBR_Bsmumu_0,2}
    % \includegraphics[width=.32\textwidth]{plots/pdf/scSP_Bsmumu,scSP_FH,sc910SP_K_KstarBR_Bsmumu_4,6}
    \includegraphics[width=.325\textwidth]{plots/pdf/scSP_FH,sc910SP_K_KstarBR_Bsmumu_0,4}
    \includegraphics[width=.325\textwidth]{plots/pdf/scSP_Bsmumu,sc910SP_K_KstarBR_Bsmumu_2,6}
  \end{center}
  \caption{ The constraints on complex-valued
    $\wilson{S,\,S',\,P,\,P'}$ from only $F_H^\mu$~(grey dotted), only
    $\overline{\cal B}(B_s \to \bar\mu\mu)$ (blue dashed), and the
    combination with all other data in \reftab{tab:observables} as
    well as nonzero $\wilson[]{9,\,9',\,10,\, 10'}$ (red solid) at
    68\% (darker) and 95\% (lighter) probability. The constraints on
    Re$(\wilson{P} \pm \wilson{P'})$ are identical to Re$(\wilson{S}
    \pm \wilson{S'})$, apart from a small translation of the contours
    by $(+0.2,\, +0.15)$. The SM prediction is indicated by the black
    diamond. }
  \label{fig:scalar}
\end{figure*}

@@

In the following we consider a scenario in which it is assumed that there is
a sizeable hierarchy between the electroweak scale and the new-physics 
scale, $\Lambda_{\rm NP}$, and that the SM gauge symmetries $SU(2)_L \times
U(1)_Y$ are only broken at the electroweak scale. This results in the
augmentation of the SM by dimension-six operators that respect the SM gauge
group and are composed of SM fields only. Such a scenario becomes more
and more viable for two reasons. The first is the discovery of a
scalar resonance at the LHC in agreement with all requirements of the
Higgs particle in the SM. The second is the steadily rising lower
bounds on the mass of new particles reported by ATLAS and CMS in
various more or less specific models.

A nonredundant set of dimension-six operators of this effective theory (SM-EFT),
requiring additionally the electroweak symmetry to be linearly realized,
was given in \cite{Grzadkowski:2010es}.  The matching of the SM-EFT to the
effective theory of $\Delta B = 1$ decays \refeq{eq:Heff} at the scale
$\mu \sim m_W$ of the order of the $W$-boson mass was performed for vector
couplings $\wilson{7,\,9,\,10}$ in~\cite{D'Ambrosio:2002ex}. The matching
of tensor \refeq{eq:tensor:ops} and scalar \refeq{eq:scalar:ops} operators 
\cite{Alonso:2014csa} shows that SM gauge groups in conjunction with the 
linear representation impose the relations
\begin{align}
  \label{eq:mEFT-constraints}
  \wilson{P}  & = -\wilson{S}\,, &
  \wilson{P'} & = \wilson{S'}\,, &
  \wilson{T}  & = \wilson{T5} = 0
\end{align}
on scalar couplings and require tensor couplings to be
suppressed to the level of dimension-eight operators. In consequence only two
scalar couplings $\wilson{S,\, S'}$ arise that scale as $(\sim v/\Lambda_{\rm
  NP})^2 \ll 1$ where $v \propto m_W$ denotes the scale of electroweak symmetry breaking.

It must be noted that the relations \refeq{eq:mEFT-constraints} are a
consequence of embedding the Higgs in a weak doublet along with the Goldstone
bosons.  For example choosing a nonlinear representation of the scalar sector
allows additional dimension-six operators in the according effective theory, 
such that the couplings $\wilson{S,S',P,P'}$ are all independent and tensor
operators have nonvanishing couplings already at dimension six 
\cite{Cata:2015lta}.

@@

\begin{figure*}
  \begin{center}
      \includegraphics[width=.35\textwidth]{plots/pdf/smEFTS_K_Bsmumu,smEFTS10_K_KstarBR_Bsmumu_0,2}
      \includegraphics[width=.35\textwidth]{plots/pdf/smEFTS_K_Bsmumu,smEFTS10_K_KstarBR_Bsmumu_1,3}
    \end{center}
    \caption{ 68\% and 95\% contours of the 2D-marginalized distributions of
      scalar couplings $\wilson{S,\,S'}$ in the scenario SM-EFT with all
      constraints in \reftab{tab:observables} (red) when marginalising over
      nonzero $\mbox{Re, Im} (\wilson[NP]{10,\,10'})$.  For comparison, we
      superimpose the corresponding contours from using only $\overline{\cal
        B}(B_s\to \bar\mu\mu)$ and all {$B \to K \bar\mu\mu$} constraints
      (dashed blue contours) with fixed $\wilson[NP]{10,\,10'} = 0$.  The SM is
      indicated by the black diamond.  \checked{}}
  \label{fig:scalar:SM-EFT}
\end{figure*}

@@

  Moreover, measurements of $F_H^e$ ($\ell = e$) will provide constraints on
  scalar couplings in the electron channel in the absence of a direct
  determination of the branching ratio of $B_s \to \bar{e}e$.
\end{enumerate}
Our updated bounds on complex-valued tensor and scalar couplings are summarised
in \reftab{tab:cTT5:1-dimCLs} and \reftab{tab:cSP:1-dimCLs}, accounting also for
interference effects with vector couplings. These bounds hold even in the most
general scenario of complex-valued tensor, scalar, and vector couplings, showing
that the data are good enough to bound the real and imaginary parts of all
Wilson coefficients simultaneously.

@@

%
%
%
%--------+---------+---------+---------+---------+---------+---------+---------+
\begin{acknowledgements}
  We are grateful to Danny van Dyk for helpful discussions and his support on
  \eos~\cite{EOS}. Concerning form factor results from lattice QCD, we thank
  Chris Bouchard and Matthew Wingate for communications on their results of
  $B\to K$ \cite{Bouchard:2013eph} and $B\to K^*$ \cite{Horgan:2015vla} form
  factors. We thank also David Straub for his support with LCSR results of $B\to
  K^*$ form factors \cite{Straub:2015ica}. We thank Martin Jung, David Straub
  and Danny van Dyk for comments on the manuscript. C.B. was supported by the ERC
  Advanced Grant project ``FLAVOUR'' (267104). We acknowledge the support by the
  DFG Cluster of Excellence "Origin and Structure of the Universe". The
  computations have been carried out on the computing facilities of the
  Computational Center for Particle and Astrophysics (C2PAP).
\end{acknowledgements}

@@

  Concerning $B_s\to \bar\ell\ell$, the expression \refeq{eq:Br-Bsmumu:time0}
  corresponds to the unintegrated branching ratio at time $t=0$. Due to the
  nonvanishing decay width $\Delta\Gamma_s$, experiments measure the average
  time-integrated branching ratio---denoted by $\overline{\cal B}$---and the two
  are related as \cite{DeBruyn:2012wk}
\begin{align}
  \label{eq:Br-Bsmumu}
  \overline{\cal B} (B_s \to \bar\ell\ell) &
  = \frac{1 + y_s {\cal A}_{\Delta\Gamma}}{1 - y_s^2} {\cal B} (B_s \to \bar\ell\ell)\,.
\end{align}
Here $y_s \equiv \Delta\Gamma_s/(2\Gamma_s)$ with the numerical value given in
\cite{Beaujean:2013soa}. ${\cal A}_{\Delta\Gamma}$ is the CP asymmetry
due to nonvanishing width difference, which is ${\cal A}_{\Delta\Gamma} = 1$
in the SM, but in general can be ${\cal A}_{\Delta\Gamma} \in [-1,\, 1]$.
Since ${\cal A}_{\Delta\Gamma}$ can depart from it's SM value in scenarios of
new physics considered in this work, we take this effect into account
in our numerical analysis, although it is suppressed by small $y_s$. The latest
SM prediction $\overline{\cal B} (B_s \to \bar\mu\mu) = (3.65 \pm 0.23) \cdot
10^{-9}$~\cite{Bobeth:2013uxa} includes NLO electroweak \cite{Bobeth:2013tba}
and NNLO QCD corrections \cite{Hermann:2013kca}.

@@

Concerning numerical input, we refer the reader to~\cite{Beaujean:2013soa} for
the compilation of nuisance parameters relevant to this work. We adopt the same
values for fixed parameters and the same priors unless noted otherwise
below. Specifically, we use identical priors for for common nuisance parameters
of the CKM quark-mixing matrix, the charm and bottom quark masses in the
$\overline{\rm MS}$ scheme, and the parameterization of subleading corrections
in $1/m_b$ as given in \cite{Beaujean:2013soa}.

@@

{Therefore, we need} additional nuisance parameters for the
complete set of $B\to K$ form factors $f_{+,T,0}$. As a consequence of using the
$z$ parameterization \cite{Khodjamirian:2010vf} and the kinematic relation
$f_0(0) = f_+(0)$, five nuisance parameters (listed in
\reftab{tab:hadronic:nuisance}) are needed. As prior information, we average the
LCSR results~\cite{Khodjamirian:2010vf} and \cite{Ball:2004ye} (see
\reftab{tab:hadronic:nuisance} and cf. \cite{Beaujean:2013soa}) supplement them
with lattice determinations~\cite{Bouchard:2013eph}.
The lattice results are given in a slightly different parametrization
necessitating a conversion to the parametrization used here. For this purpose,
we generate the form factors from the parametrization
of~\cite{Bouchard:2013eph}, including full correlations, at three values of $q^2
= 17,\, 20,\, 23$ GeV$^2$.  Subsequently, these ``data'' are included in the
prior by means of a multivariate Gaussian whose mean and covariance is given in
\reftab{tab:btok-lattice}. The $q^2$ values and number of points are chosen such
that the correlation of neighboring points is small enough to keep the
covariance nonsingular.

@@

We have compared the SSE fit \refeq{eq:SSE-FF-parameterization} with two versus
three parameters and found that in the former case lattice form factors
influence the fit such that form factors tend to be higher than LCSR predictions
at low $q^2$ leading to a poor fit. Hence we prefer the three-parameter setup as
it provides the flexibility needed to accomodate LCSR and lattice results. Means
and standard {deviations} of that three-parameter fit are given in
\reftab{tab:hadronic:nuisance}, we omit the correlations for the sake of brevity
but are happy to provide them.

>>>>

The full dependence of $F_H^\ell$ and $A_{\rm FB}^\ell$ on tensor and
scalar couplings has been presented in \cite{Bobeth:2007dw,
  Bobeth:2012vn}, adopting the effective theory \refeq{eq:Heff},
i.e. neglecting higher-dimensional operators with {$\mbox{dim} \geq
  8$}. These results imply that for SM values of the effective
couplings
\begin{align}
  F_H^\ell(q^2) \big|_{\rm SM} & \propto \frac{m_\ell^2}{q^2}
    {\bigg/ \Gamma_\ell} \,, &
  A_{\rm FB}^\ell \big|_{\rm SM} & = 0 \,.
\end{align}
Hence, for $\ell = e,\, \mu$ both observables are quasi-null tests.
The flat term $F_H^\ell(q^2)|_{\rm SM}$ is strongly suppressed {by
  small lepton masses for the considered kinematic region $1 \leq
  q^2 \leq 22$ GeV$^2$} \cite{Bobeth:2007dw, Bobeth:2011nj,
  Bouchard:2013eph}.  Nonzero values of $A_{\rm FB}^\ell|_{\rm SM}$
can be induced by higher-order QED corrections, which will modify the
simple $\cos\theta_\ell$ dependence of the angular
distribution~\refeq{eq:ang-distr}, however, currently there is no
solid estimate available for this source of SM background\footnote{
  Logarithmically enhanced NLO QED corrections to $B\to X_s
  \bar\ell\ell$~\cite{Huber:2015sra} turn out to be non-negligible
  for angular observables,
  however, analogous corrections to $B\to K \bar\ell\ell$ are partially
  included in the event simulation of the experimental
  analysis~\cite{Aaij:2014tfa} via PHOTOS~\cite{Golonka:2005pn}.
  As proposed in \cite{Gratrex:2015hna}, the measurement of higher
  moments of the decay distribution~\refeq{eq:ang-distr} could give an
  estimate of the size of higher-order QED corrections, but still
  admixed with contributions of $\mbox{dim} \geq 8$ operators.}.
This picture does not change in the presence of new physics contributions to
vector and dipole operators $i = 7,7',9,9',10,10'$. On the other hand,
nonvanishing tensor or scalar contributions are enhanced unless the dynamics of
NP implies similar suppression factors, i.e., lepton-Yukawa couplings for
$F_H^\ell$ or $\alpha_e$ in the case of $A_{\rm FB}^\ell$. In particular,
$F_H^\ell$ is very sensitive to tensor couplings (see \refeq{eq:AFB-dependence}
below) and $A_{\rm FB}^\ell$ is sensitive to the interference of tensor and
scalar couplings (see \refeq{eq:FH-dependence} below).

\begin{figure*}
  \setlength{\relwidth}{0.33\textwidth}
  \begin{center}
    \includegraphics[width=\relwidth]{plots/pdf/ct_K_FH1to6}
    \includegraphics[width=\relwidth]{plots/pdf/ct_K_FH15to22}
    \\
    \includegraphics[width=\relwidth]{plots/pdf/ct_K_BR1to6}
    \includegraphics[width=\relwidth]{plots/pdf/ct_K_BR15to22}
    \\
    \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_BR1to6}
    % \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_BR14to16}
    \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_BR16to19}
    \\
    \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_J_1c_plus_J_2c1to6}
    \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_J_1c_plus_J_2c15to19}
    \\
    \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_J_1s_minus_3J_2s1to6}
    \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_J_1s_minus_3J_2s15to19}
  \end{center}
  \caption{ The sensitivity to the tensor coupling
    $\mbox{Re}(\wilson{T})$ of $F_H^\mu$ and {${\cal B}_\mu$} in $B^+
    \to K^+ \bar\mu\mu$ {as well as} {${\cal B}_\mu$},
    $(J_{1c} + J_{2c})$, and $(J_{1s}-3 J_{2s})$ in $B^0 \to K^{*0}
    \bar\mu\mu$. All observables are integrated over $q^2$ bins as
    $\langle \dots \rangle_{[q^2_{\rm min}, q^2_{\rm max}]}$. Angular
    observables are rescaled by the lifetime of the $B$ meson,
    $\tau_B$. The bands represent the theory uncertainties at 68\% and
    95\% probability of the prior predictive.  Two sets of bands are
    shown for $\wilson[NP]{9} = 0$ (blue) and $\wilson[NP]{9} = -1.1$
    (red). If available, the gray band indicates the latest 68\%
    confidence interval reported by LHCb.}
  \label{fig:FHvsCT}
\end{figure*}

@@

For each coupling {that} we vary in a fit, we remain as general as possible, treat it
as a complex number and use the Cartesian parametrization assuming uniform
priors for ease of comparison with previous studies. Specifically, we set
\begin{align}
  \label{eq:wilson-prior}
  \mbox{Re}(\wilson{S,S',P,P',T,T5}) &\in [-1, 1],\nn \mbox{Re}(\wilson{9,9',10,10'}) &\in [-7, 7],
\end{align}
and the same for the imaginary parts. The priors of the nuisance parameters are given in \refapp{app:theory:inputs}.

@@

In a scenario with only {complex-valued tensor couplings} $\wilson{T,\, T5}$, the
experimental measurement of $F_H^\mu$ constrains the combination $|\wilson{T}|^2
+ |\wilson{T5}|^2$, up to some small interference of $\wilson{T}$ with vector
couplings $\wilson{7,\,7',\,9,\,9'}$; cf. \refeq{eq:FH-dependence}.  The
according 68\% (95\%) 1D-marginalized probability intervals are listed in the
second column of \reftab{tab:cTT5:1-dimCLs}. From the third column, it is seen
that the constraints become tighter when utilizing all observables in
\reftab{tab:observables}, mainly due to the sensitivity of the branching ratio
of $B\to K^{*} \bar\mu\mu$ to tensor couplings (see also
\reffig{fig:FHvsCT}). The latter stronger bounds are driven by the new lattice
results of $B\to K^*$ form factors that predict values above the measured
{ones}~\cite{Horgan:2013pva}. Since tensor couplings contribute constructively
to ${\cal B}(B\to K^{*}\bar\mu\mu)$, large values are better constrained. In
this scenario with vanishing scalar couplings, current measurements of $A_{\rm
  FB}^\mu(B^+\to K^+\bar\mu\mu)$ barely provide any constraint;
cf.~\refeq{eq:AFB-dependence}.

@@

A keen observer may notice that in \reftab{tab:cTT5:1-dimCLs} the SM point
$\wilson{T,T5} \equiv 0$ is contained in every 68\% region in Cartesian
coordinates but never in even the 95\% region in polar coordinates\footnote{But
  the bin with lower edge $\wilson{T,T5} = 0$ is always in the 99\%
  region.}. This is a consequence of the general \emph{concentration of
  measure}. Another way to look at it is to transform the uniform prior density
from Cartesian to polar coordinates. For the example of a single Wilson
coefficient, say $\wilson{T}$, the transformed density is proportional to the
determinant of the Jacobian which is $|\wilson{T}|$. Since the Cartesian prior
boundaries are much larger than the regions of high likelihood, one could think
the value of the boundary is irrelevant, but in fact it determines the peak of
the prior in polar coordinates. In other words, the uniform prior on
$\mbox{Re}(\wilson{T})$ and $\mbox{Im}(\wilson{T})$ favors larger values of
$|\wilson{T}|$ even though we consider it consensus in the community that
smaller rather than larger values are reasonable because $\wilson{T} = 0$ in the
SM. We suggest therefore that the default treatment be revised in the future to
include available prior knowledge.

@@

\begin{figure*}
  \begin{center}
    \includegraphics[width=.325\textwidth]{plots/pdf/scSP_FH,scSP_Bsmumu,sc910SP_K_KstarBR_Bsmumu_0,2}
    % \includegraphics[width=.32\textwidth]{plots/pdf/scSP_Bsmumu,scSP_FH,sc910SP_K_KstarBR_Bsmumu_4,6}
    \includegraphics[width=.325\textwidth]{plots/pdf/scSP_FH,sc910SP_K_KstarBR_Bsmumu_0,4}
    \includegraphics[width=.325\textwidth]{plots/pdf/scSP_Bsmumu,sc910SP_K_KstarBR_Bsmumu_2,6}
  \end{center}
  \caption{ The constraints on complex-valued
    $\wilson{S,\,S',\,P,\,P'}$ from only $F_H^\mu$~(gray dotted), only
    $\overline{\cal B}(B_s \to \bar\mu\mu)$ (blue dashed), and the
    combination with all other data in \reftab{tab:observables} as
    well as nonzero $\wilson[]{9,\,9',\,10,\, 10'}$ (red solid) at
    68\% (darker) and 95\% (lighter) probability. The constraints on
    Re$(\wilson{P} \pm \wilson{P'})$ are identical to Re$(\wilson{S}
    \pm \wilson{S'})$, apart from a small translation of the contours
    by $(+0.2,\, +0.15)$. The SM prediction is indicated by the black
    diamond. }
  \label{fig:scalar}
\end{figure*}

@@

In the following we consider a scenario in which it is assumed that there is
a sizable hierarchy between the electroweak scale and the new-physics
scale, $\Lambda_{\rm NP}$, and that the SM gauge symmetries $SU(2)_L \times
U(1)_Y$ are only broken at the electroweak scale. This results in the
augmentation of the SM by dimension-six operators that respect the SM gauge
group and are composed of SM fields only. Such a scenario becomes more
and more viable for two reasons. The first is the discovery of a
scalar resonance at the LHC in agreement with all requirements of the
Higgs particle in the SM. The second is the steadily rising lower
bound on the mass of new particles reported by ATLAS and CMS in
various more or less specific models.

A nonredundant set of dimension-six operators of this effective theory (SM-EFT)
that requires a linear realization of the electroweak symmetry was given in
\cite{Grzadkowski:2010es}.  The matching of the SM-EFT to the effective theory
of $\Delta B = 1$ decays \refeq{eq:Heff} at the scale $\mu \sim m_W$ of the
order of the $W$-boson mass was performed for vector couplings
$\wilson{7,\,9,\,10}$ in~\cite{D'Ambrosio:2002ex}. The matching of tensor
\refeq{eq:tensor:ops} and scalar \refeq{eq:scalar:ops} operators
\cite{Alonso:2014csa} shows that SM gauge groups in conjunction with the linear
representation impose the relations
\begin{align}
  \label{eq:mEFT-constraints}
  \wilson{P}  & = -\wilson{S}\,, &
  \wilson{P'} & = \wilson{S'}\,, &
  \wilson{T}  & = \wilson{T5} = 0
\end{align}
on scalar couplings and require tensor couplings to be
suppressed to the level of dimension-eight operators. In consequence only two
scalar couplings $\wilson{S,\, S'}$ arise that scale as $(\sim v/\Lambda_{\rm
  NP})^2 \ll 1$ where $v \propto m_W$ denotes the scale of electroweak symmetry breaking.

It must be noted that the relations \refeq{eq:mEFT-constraints} are a
consequence of embedding the Higgs in a weak doublet along with the Goldstone
bosons.  For example, choosing a nonlinear representation of the scalar sector
allows additional dimension-six operators in the according effective theory,
such that the couplings $\wilson{S,S',P,P'}$ are all independent and tensor
operators have nonvanishing couplings already at dimension six
\cite{Cata:2015lta}.

@@

\begin{figure*}
  \begin{center}
      \includegraphics[width=.35\textwidth]{plots/pdf/smEFTS_K_Bsmumu,smEFTS10_K_KstarBR_Bsmumu_0,2}
      \includegraphics[width=.35\textwidth]{plots/pdf/smEFTS_K_Bsmumu,smEFTS10_K_KstarBR_Bsmumu_1,3}
    \end{center}
    \caption{ 68\% and 95\% contours of the 2D-marginalized distributions of
      scalar couplings $\wilson{S,\,S'}$ in the scenario SM-EFT with all
      constraints in \reftab{tab:observables} (red) when marginalizing over
      nonzero $\mbox{Re, Im} (\wilson[NP]{10,\,10'})$.  For comparison, we
      superimpose the corresponding contours from using only $\overline{\cal
        B}(B_s\to \bar\mu\mu)$ and all {$B \to K \bar\mu\mu$} constraints
      (dashed blue contours) with fixed $\wilson[NP]{10,\,10'} = 0$.  The SM is
      indicated by the black diamond.  \checked{}}
  \label{fig:scalar:SM-EFT}
\end{figure*}

@@

  Moreover, measurements of $F_H^e$ ($\ell = e$) will provide constraints on
  scalar couplings in the electron channel in the absence of a direct
  determination of the branching ratio of $B_s \to \bar{e}e$.
\end{enumerate}
Our updated bounds on complex-valued tensor and scalar couplings are summarized
in \reftab{tab:cTT5:1-dimCLs} and \reftab{tab:cSP:1-dimCLs}, accounting also for
interference effects with vector couplings. These bounds hold even in the most
general scenario of complex-valued tensor, scalar, and vector couplings, showing
that the data are good enough to bound the real and imaginary parts of all
Wilson coefficients simultaneously.

@@

%
%
%
%--------+---------+---------+---------+---------+---------+---------+---------+
\begin{acknowledgements}
  We are grateful to Danny van Dyk for helpful discussions and his support on
  \eos~\cite{EOS}. Concerning form factor results from lattice QCD, we thank
  Chris Bouchard and Matthew Wingate for communications on their results of
  $B\to K$ \cite{Bouchard:2013eph} and $B\to K^*$ \cite{Horgan:2015vla} form
  factors. We thank also David Straub for his support with LCSR results of $B\to
  K^*$ form factors \cite{Straub:2015ica}. We thank Martin Jung, David Straub,
  and Danny van Dyk for comments on the manuscript. C.B. was supported by the ERC
  Advanced Grant project ``FLAVOUR'' (267104). We acknowledge the support by the
  DFG Cluster of Excellence "Origin and Structure of the Universe". The
  computations have been carried out on the computing facilities of the
  Computational Center for Particle and Astrophysics (C2PAP).
\end{acknowledgements}

@@

  Concerning $B_s\to \bar\ell\ell$, the expression \refeq{eq:Br-Bsmumu:time0}
  corresponds to the plain branching ratio at time $t=0$. Due to the
  nonvanishing decay width $\Delta\Gamma_s$, experiments measure the average
  time-integrated branching ratio---denoted by $\overline{\cal B}$---and the two
  are related as \cite{DeBruyn:2012wk}
\begin{align}
  \label{eq:Br-Bsmumu}
  \overline{\cal B} (B_s \to \bar\ell\ell) &
  = \frac{1 + y_s {\cal A}_{\Delta\Gamma}}{1 - y_s^2} {\cal B} (B_s \to \bar\ell\ell)\,.
\end{align}
Here $y_s \equiv \Delta\Gamma_s/(2\Gamma_s)$ with the numerical value given in
\cite{Beaujean:2013soa}. ${\cal A}_{\Delta\Gamma}$ is the CP asymmetry
due to nonvanishing width difference, which is ${\cal A}_{\Delta\Gamma} = 1$
in the SM, but in general can be ${\cal A}_{\Delta\Gamma} \in [-1,\, 1]$.
Since ${\cal A}_{\Delta\Gamma}$ can depart from it's SM value in scenarios of
new physics considered in this work, we take this effect into account
in our numerical analysis, although it is suppressed by small $y_s$. The latest
SM prediction $\overline{\cal B} (B_s \to \bar\mu\mu) = (3.65 \pm 0.23) \cdot
10^{-9}$~\cite{Bobeth:2013uxa} includes NLO electroweak \cite{Bobeth:2013tba}
and NNLO QCD corrections \cite{Hermann:2013kca}.

@@

Concerning numerical input, we refer the reader to~\cite{Beaujean:2013soa} for
the compilation of nuisance parameters relevant to this work. We adopt the same
values for fixed parameters and the same priors unless noted otherwise
below. Specifically, we use identical priors for for common nuisance parameters
of the CKM quark-mixing matrix, the charm and bottom quark masses in the
$\overline{\rm MS}$ scheme, and the parametrization of subleading corrections
in $1/m_b$ as given in \cite{Beaujean:2013soa}.

@@

{Therefore, we need} additional nuisance parameters for the
complete set of $B\to K$ form factors $f_{+,T,0}$. As a consequence of using the
$z$ parametrization \cite{Khodjamirian:2010vf} and the kinematic relation
$f_0(0) = f_+(0)$, five nuisance parameters (listed in
\reftab{tab:hadronic:nuisance}) are needed. As prior information, we average the
LCSR results~\cite{Khodjamirian:2010vf} and \cite{Ball:2004ye} (see
\reftab{tab:hadronic:nuisance} and cf. \cite{Beaujean:2013soa}) supplement them
with lattice determinations~\cite{Bouchard:2013eph}.
The lattice results are given in a slightly different parametrization
necessitating a conversion to the parametrization used here. For this purpose,
we generate the form factors from the parametrization
of~\cite{Bouchard:2013eph}, including full correlations, at three values of $q^2
= 17,\, 20,\, 23$ GeV$^2$.  Subsequently, these ``data'' are included in the
prior by means of a multivariate Gaussian whose mean and covariance is given in
\reftab{tab:btok-lattice}. The $q^2$ values and number of points are chosen such
that the correlation of neighboring points is small enough to keep the
covariance nonsingular.

@@

We have compared the SSE fit \refeq{eq:SSE-FF-parametrization} with two versus
three parameters and found that in the former case lattice form factors
influence the fit such that form factors tend to be higher than LCSR predictions
at low $q^2$ leading to a poor fit. Hence we prefer the three-parameter setup as
it provides the flexibility needed to accommodate LCSR and lattice results. Means
and standard {deviations} of that three-parameter fit are given in
\reftab{tab:hadronic:nuisance}, we omit the correlations for the sake of brevity
but are happy to provide them.
